opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-26 chapters/02_existing_datasets.tex
Commented out statement that pearson and PDF have huge overlap

\textbf{Pearson's Crystal data}:\footnote{More information on Pearson's crystal data can be found on the ASM International website under \url{https://www.asminternational.org/materials-resources/online-databases/pearsons-crystal-data-crystal-structure-database-for-inorganic-compounds/?srsltid=AfmBOorjpwJSVNsaWtCO4kmgu-Ox2ncF3tkzwCXRE2GTemYIxsSLp8xr}.} Pearson's crystal data is a commercial database of 395,000 crystal structures including 21,700 experimental powder diffraction patterns maintained by ASM International first published in 2003.\footnote{According to CrystalImpact, who acts as distributor for Pearson's crystal data. For more information refer to the CrystalImpact website under \url{https://web.archive.org/web/20241112132017/https://www.crystalimpact.com/news/Default.htm}. } Pearson's crystal data is based on the data of another crystal structure database, the Linus Pauling file \cite{kaduk2007}. Since the Linus Pauling file is also a database source for the PDF, there is likely a significant overlap between the experimental powder diffraction data found in Pearson's crystal data and that found in the PDF. As of November 2024, Pearson's crystal data is available to researchers through a purchase of a one-year license starting at a price point of 2200 \euro.\\

>>>>

\textbf{Pearson's Crystal data}:\footnote{More information on Pearson's crystal data can be found on the ASM International website under \url{https://www.asminternational.org/materials-resources/online-databases/pearsons-crystal-data-crystal-structure-database-for-inorganic-compounds/?srsltid=AfmBOorjpwJSVNsaWtCO4kmgu-Ox2ncF3tkzwCXRE2GTemYIxsSLp8xr}.} Pearson's crystal data is a commercial database of 395,000 crystal structures including 21,700 experimental powder diffraction patterns maintained by ASM International first published in 2003.\footnote{According to CrystalImpact, who acts as distributor for Pearson's crystal data. For more information refer to the CrystalImpact website under \url{https://web.archive.org/web/20241112132017/https://www.crystalimpact.com/news/Default.htm}. }As of November 2024, Pearson's crystal data is available to researchers through a purchase of a one-year license starting at a price point of 2200 \euro.\\

% TODO: I need to check that by asking
%Pearson's crystal data is provided by the Pauling File project which also provides the Materials Phases Data System database (MPDS). 
%Since the MPDS is listed as a database source for the PDF5+ \cite{kaduk2007}, there is likely a significant overlap between the experimental powder diffraction data found in Pearson's crystal data and that found in the PDF. 
 %\tablefootnote{The PDF and Pearson's Crystal data both derive some of their data from the Linus Pauling File, which has a similar number of experimental powder diffraction patterns as both the PDF and Pearson's Crystal Data. Hence there is likely significant overlap in the patterns available in the PDF and in Pearson's crystal data.}
